---
title: "test-1"
format: html
---




## New project 1

#### This is new
Here is the new project!


```{r}
# setup

library(tidyverse)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

A choropleth map is a type of thematic map in which a set of pre-defined areas is colored or patterned in proportion to a statistical variable that represents an aggregate summary of a geographic characteristic within each area, such as population density or per-capita income.

First let's get familiar with the `map_data` function. This function can easily turn data from the `maps` package into a data frame that is suitable for plotting with `ggplot2`. This functions contains maps of several countries including 'France', 'Italy' and many maps of 'USA'. Please see the description to learn more about this.

```{r}
library(tidyverse)
```

```{r echo=FALSE}
hw <- theme_gray()+ theme(
  plot.title=element_text(hjust=0.5),
  plot.subtitle=element_text(hjust=0.5),
  plot.caption=element_text(hjust=-.5),

  strip.text.y = element_blank(),
  strip.background=element_rect(fill=rgb(.9,.95,1),
    colour=gray(.5), linewidth =.2),

  panel.border=element_rect(fill=FALSE,colour=gray(.70)),
  panel.grid.minor.y = element_blank(),
  panel.grid.minor.x = element_blank(),
  panel.spacing.x = unit(0.10,"cm"),
  panel.spacing.y = unit(0.05,"cm"),

# axis.ticks.y= element_blank()
  axis.ticks=element_blank(),
  axis.text=element_text(colour="black"),
  axis.text.y=element_text(margin=margin(0,3,0,3)),
  axis.text.x=element_text(margin=margin(-1,0,3,0))
)
```

# Tutorial

In this example let's try to extract data from a "world map" and try to plot it using `ggplot`.

```{r}
#extracting data and saving as a tibble
world_tbl <- map_data("world") %>% as_tibble()
world_tbl
```

Now with the `world_tbl`, let's try to visualize it.

```{r}
world_base <- world_tbl %>%
  ggplot() +
  geom_map(
    aes(long, lat, map_id = region),
    map = world_tbl,
    color = "gray80", fill = "gray30", size = 0.3) + hw
world_base
```

Notice that this is a "Mercator" Projection of the 'World Map'. But if you want a different projection, such as 'Orthogonal Projection" you can use the following commands. In order to learn about different maps projections can be used in `ggplot2` please use the following this [link.](https://rdrr.io/cran/mapproj/man/mapproject.html)

```{r}
world_base +
  coord_map("ortho", orientation = c(39, -98, 0))
```

By changing the `orientation` coordinates above, you should be able to rotate the globe on X, Y and Z axes.

Now let's look at a map of 'USA' with 'orthogonal projection'.

```{r}
usa_tbl <- map_data("state") %>% as_tibble()

usa_tbl %>%
  ggplot(aes(long, lat, map_id = region)) +
  geom_map(
    map = usa_tbl,
    color = "gray80", fill = "gray30", size = 0.3) +
  coord_map("ortho", orientation = c(39, -98, 0)) +hw
```

# Example 1 : EU Vaccination Data



